---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hrm

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R build status](https://github.com/jasenfinch/hrm/workflows/R-CMD-check/badge.svg)](https://github.com/jasenfinch/hrm/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/jasenfinch/hrm/master.svg)](https://codecov.io/github/jasenfinch/hrm?branch=master)
<!-- badges: end -->

Easily install, load and update an R package ecosystem for performing analyses of high resolution metabolomics data.

`hrm` packages include:

* [metaboData](https://aberHRML.github.io/metaboData) - Example data sets for metabolomics analyses
* [grover](https://jasenfinch.github.io/grover) - Web API Framework for Mass Spectrometry Data Transfer
* [binneR](https://aberHRML.github.io/binneR) - Spectral Processing for High Resolution Flow Infusion Mass Spectrometry
* [metabolyseR](https://jasenfinch.github.io/metabolyseR) - A tool kit for pre-treatment, modelling, feature selection and correlation analyses of metabolomics data
* [profilePro](https://jasenfinch.github.io/profilePro) - Unified Input and Output for Processing of Metabolomic Profiling Experiments
* [mzAnnotation](https://jasenfinch.github.io/mzAnnotation) -  Tools for putative annotation of accurate m/z from electrospray ionisation mass spectrometry data
* [MFassign](https://github.com/jasenfinch/MFassign) - Molecular formula assignment for high resolution ESI metabolomics
* [construction](https://github.com/jasenfinch/construction) - Consensus structural classifications for putative molecular formula assignments
* [composition](https://github.com/jasenfinch/composition) - Compositional analyses for metabolomics data
* [riches](https://jasenfinch.github.io/riches) - Structural and functional enrichment for metabolomics data
* [metaboMisc](https://jasenfinch.github.io/metaboMisc) - A collection of miscellaneous helper and linker functions for metabolomics analyses
* [metaboWorkflows](https://jasenfinch.github.io/metaboWorkflows) - Workflow Project Templates for Metabolomics Analyses

## Installation

Install the `hrm` package from GitHub using:

```{r,eval=FALSE}
remotes::install_github('jasenfinch/hrm')
```

### Usage

Loading the `hrm` packages will load the included R packages.

```{r load}
library(hrm)
```

Alteratively, these packages can be loaded using the following, without loading the `hrm` package directly.

```{r load_alt,eval=FALSE}
hrm::hrmAttach()
```

A vector of the current `hrm` packages can be found by:

```{r packages}
hrmPackages()
```

`hrm` associated packages can be updated using:

```{r update,eval=FALSE}
hrmUpdate()
```
