---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hrm

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/jasenfinch/hrm/workflows/R-CMD-check/badge.svg)](https://github.com/jasenfinch/hrm/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/jasenfinch/hrm/master.svg)](https://codecov.io/github/jasenfinch/hrm?branch=master)
<!-- badges: end -->

Easily install, load and update an R package ecosystem for performing analyses of high resolution metabolomics data.

`hrm` packages include:

* [metaboData](https://github.com/aberHRML/metaboData)
* [binneR](https://github.com/aberHRML/binneR)
* [metabolyseR](https://github.com/jasenfinch/metabolyseR)
* [profilePro](https://github.com/jasenfinch/profilePro)
* [mzAnnotation](https://github.com/jasenfinch/mzAnnotation)
* [MFassign](https://github.com/jasenfinch/MFassign)
* [construction](https://github.com/jasenfinch/construction)
* [composition](https://github.com/jasenfinch/composition)
* [riches](https://github.com/jasenfinch/riches)
* [metaboMisc](https://github.com/jasenfinch/metaboMisc)
* [metaboWorkflows](https://github.com/jasenfinch/metaboWorkflows)
* [metaboReports](https://github.com/jasenfinch/metaboReports)


## Installation

Install the `hrm` package from GitHub using:

```{r,eval=FALSE}
remotes::install_github('jasenfinch/hrm')
```

### Usage

Loading the `hrm` packages will load the included R packages.

```{r load}
library(hrm)
```

Alteratively, these packages can be loaded using the following, without loading the `hrm` package directly.

```{r load_alt,eval=FALSE}
hrm::hrmAttach()
```

A vector of the current `hrm` packages can be found by:

```{r packages}
hrmPackages()
```

`hrm` associated packages can be updated using:

```{r update,eval=FALSE}
hrmUpdate()
```
